Chapter X : Review of Methods for Solving the AX\raisebox{.2ex}{=}XB Sensor Calibration Problem

### 2015-09-02 AXXB_Review/AXXB Review.tex
Adjusted Manuscript for the Review Chapter of Humanoid Robotics : A Reference

\author{Qianli Ma\thanks{Address all correspondence to this author.}\\ 
		\textbf{Gregory S. Chirikjian}
    \affiliation{
	Robot and Protein Kinematics Laboratory\\
	Laboratory for Computational Sensing and Robotics\\
	Department of Mechanical Engineering\\
	The Johns Hopkins University\\
	Baltimore, Maryland, 21218\\
    Email: \{mqianli1, gchirik1\}@jhu.edu
    }	
}

@@

\keywords{Sensor Calibration, Hand-Eye Calibration, Humanoid Robot, Review}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{nomenclature}
\entry{\textcolor{blue}{Note}}{\textcolor{blue}{For SE(3) and se(3) maybe make the inline matrices into actual matrices, it looks a little strange to me the way they are currently. Also, possibly consider changing $\Xi$ to $\mathfrak{h}$. Also, can you align the beginning of all of the second entries?}}
\entry{$SO(3)$}{$SO(3) \doteq \{R \, | \, RR^{T} = R^{T}R = \mathbb{I}$\textbf{\textcolor{blue}{,}} %and
 $\det(R) = 1$\textbf{\textcolor{blue}{,}} where $R \in \mathbb{R}^{3 \times 3}\}$}
\entry{$SE(3)$}{$SE(3) \doteq \{H \, | \, H=\left( R \;   \ttt ; {\bf 0}^{T} 1 \right) \in \mathbb{R}^{4 \times 4},$ where $R \in SO(3)$ and $\ttt \in \mathbb{R}^{3}\}$ }
\entry{$so(3)$}{$so(3) \doteq \{\Omega \,| \, R = exp(\Omega)$, where $\Omega \in \mathbb{R}^{3 \times 3}$ and $R \in SO(3)$ $\}$}
\entry{$se(3)$}{$se(3) \doteq \{\Xi \, | \, H = exp(\Xi)$, where $\Xi =\left(\Omega \; \xi; \; {\bf 0}^{T} 0 \right)$ and $\Omega \in \textcolor{blue}{so}%SO
(3), \, \xi \in \mathbb{R}^{3}, \, H \in SE(3) \}$}
\entry{$\exp()$}{The matrix exponential of a square matrix. }
\entry{$\log()$}{The matrix logarithm of a square matrix}
\entry{$H$}{A general rigid body transformation ($H \in SE(3)$) }
\entry{$\mathfrak{H}$}{ If $H$ is an element of a Lie Group, $\mathfrak{H}$ is the corresponding element in the Lie algebra}
\entry{$\mathbb{O}_n$}{$n \times n$ zero matrix}
\entry{$\mathbb{I}_n$}{$n \times n$ identity matrix}
\entry{$\{E_i\}$}{the set of ``natural" basis elements for Lie algebra}
\entry{$^\vee$}{For Lie algebra, the ``vee" operator is defined such that $\left(\displaystyle\sum\limits_{i=1}^n x_iE_i\right)^{\vee}\doteq(x_1,x_2,...,x_n)^T$ where $n = 3$ for $so(3)$ and $n = 6$ for $se(3)$}
\entry{$\widehat{}$}{For Lie algebra, the ``hat" operator is the inverse of the ``vee" operator. $\widehat{(x_1,x_2,...,x_n)^T} \doteq \left( \displaystyle\sum\limits_{i=1}^n x_iE_i \right)$; For a vector ${\bf n} \in \mathbb{R}^{3 \times 1}$. $\widehat{\bf n}$ represents the corresponding skew symmetric matrix }
\entry{$\circ$}{The operator defined for the group product}
\entry{$\odot$}{The operator defined for the quaternion product}
\entry{$\hat{\odot}$}{The operator defined for the dual quaternion product}
\entry{$\otimes$}{The operator defined for the Kronecker product}
\entry{$vec$}{The ``vec'' operator is defined such that $vec(A) = [a_{11},...,a_{1m},a_{21},...,a_{2m},...,a_{n1},...,a_{nm}]^{T}$ for $A = [a_{ij}] \in \mathbb{R}^{m \times n}$}
\entry{$A_i$}{A rigid body transformation ($A_i \in SE(3)$), associated with one sensor measurement source}
\entry{$B_i$}{A rigid body transformation ($B_i \in SE(3)$), usually associated with a different sensor measurement source}
\entry{$X$}{The rigid body transformation ($X %X_i 
\in SE(3)$) that relates $A_i$ to $B_i$}
\entry{$R_{H}$}{The rotation matrix of any general transformation matrix $H \in SE(3)$}
\entry{$\ttt_{H}$}{The translation vector of any general transformation matrix $H \in SE(3)$}
\entry{$\nn_{H}$}{The axis of rotation for $R_{H}$}
\entry{$\widetilde{\nn}$}{The skew-symmetric representation of the axis of rotation ($\nn_{H}$) \textcolor{blue}{If you use $\Omega$ earlier you should try to keep some continuity}}
\entry{$\theta_{H}$}{The angle of rotation for $R_{H}$ about $\nn_{H}$}
\entry{$\rho$}{A probability distribution of $H\in G$, where G $\subset$ SE(3)}
\entry{$M$}{For $\rho$, $M$ is the mean of the distribution}
\entry{$\Sigma$}{For $\rho$, $\Sigma$ is the covariance of the distribution about the mean, $M$}
\entry{$Ad$}{For the Lie group $G$ and the Lie algebra $\mathfrak{G}$, the adjoint operator is the transformation\\ Ad: $G \rightarrow$ GL($\mathfrak{G}$), defined as\\ Ad($H_1$)$\mathfrak{H}_2 \doteq \frac{d}{dt}(H_1 \circ e^{t \mathfrak{H}_2} \circ H_1^{-1})$}
\entry{$Ad(H) $}{The adjoint matrix with columns $(H E_i H^{-1})^{\vee}$}
\end{nomenclature}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
\label{Intro}
\textcolor{blue}{General Note: Shouldn't alway equations be numbered in an ASME document? It may be IEEE, but I'm just checking}\\

@@

\textcolor{blue}{This seems like an awkward transition. Can you add a sentence connecting the two paragraphs?}

@@

\begin{figure}[t]
\includegraphics[width=3.3in]{figure/AX=XB(ASME)_v1.png}
\centering
\caption{\textcolor{blue}{Increase the size of text in the image} The AX=XB Sensor Calibration Formulation}
\label{AXXBfig1}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.3in]{Photos/UR5_Frame_Final.jpg}
\caption{Application of AX=XB in ultrasound sensor calibration: an ultrasound probe is attached to the end-effector and the calibration phantom is used for ultrasound probe calibration. (The UR5 robot pictured above is owned by Professor Emad Boctor of Johns Hopkins University)}
\label{AXXBfig2}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.3in]{Photos/Robot_Patern.jpg}
\caption{\textcolor{blue}{Labels are hard to see in the picture. Also, you change the capitalization style midway through} Application of AX=XB in Humanoid Camera Sensor Calibration: The Humanoid Robot Named Atlas Designed by %the Company
 \textit{Boston Dynamics} Requires head-body calibration before turning the knob. Different pairs of $(A_i, B_i)$ are measured by changing the head pose of the humanoid robot. (This picture was generated using the open-source robot simulation software Gazebo)}
\label{AXXBfig3}
\end{figure}

Performing the matrix multiplication of homogeneous transformations in Eq.~(\ref{mainaxxb}) and separating out the rotational and translational parts results in two equations of the form:
\begin{subequations}
\begin{gather}
R_A R_X = R_X R_B \label{subequ1}\\
R_A {\bf t}_X + {\bf t}_A = R_X {\bf t}_B + {\bf t}_X \label{subequ2}.
\end{gather}
\label{axxb}
\end{subequations}
\textcolor{blue}{One strategy for solving Eq.~(\ref{mainaxxb}) reduces to first solving Eq.~(\ref{subequ1}) for only rotation and then rearranging Eq.~(\ref{subequ2}) to find acceptable values of ${\bf t}_X$ satisfying $ (R_A - \mathbb{I}_{3}) {\bf t}_X = R_X {\bf t}_B - {\bf t}_A$.}
%One strategy to solve Eq.~(\ref{mainaxxb}) \textcolor{blue}{of data}would appear to reduce to first solving Eq.~(\ref{subequ1}) for only rotation and then rearranging Eq.~(\ref{subequ2}) so as to find acceptable values of ${\bf t}_X$ satisfying $ (R_A - \mathbb{I}_{3}) {\bf t}_X = R_X {\bf t}_B - {\bf t}_A. $  
The other strategy is to solve for $R_{X}$ and $\ttt_{X}$ simultaneously based on some cost function $f(R_{X}, \ttt_{X})$ or reformulating the matrix equation into \textcolor{blue}{a dual quaternion representation}. %dual quaternion. 
However, when there are only two exact sensor measurements, there are some problems with the first  approach. As pointed out in \cite{park1994robot,shiu1989calibration}, in nondegenerate cases, there is a one-parameter set of solutions to \textcolor{blue}{Eq.~\ref{subequ1}}%the first part in Eq.(\ref{subequ1})
, and the matrix $R_A - \mathbb{I}_{3}$ in general has a rank of $2$. Hence, there are two unspecified degrees of freedom to the
problem, and it cannot be solved uniquely unless additional measurements are taken.

@@

%A wide variety of such metrics are discussed in \cite{axxb13} that have the useful property of left-invariance, $d(H_0 H_1, H_0 H_2) = d(H_1, H_2)$ for any $H_0, H_1, H_2 \in SE(3)$.
%
%
%Perhaps the simplest of the left-invariant ones is based on the weighted Frobenius norm
%$$ d^2(H_1,H_2) = \|H_1 - H_2\|_{W}^{2} = {\rm trace}[(H_1 - H_2)W(H_1 - H_2)^T] $$
%where $W$ is a matrix that weights rotations and translations appropriately, as described in \cite{axxb13}.
%The sets of pairs $(A_i,B_i)$ for $i=1,2...,n$ is chosen such
%that the set $\{A_i\}$ is spread out over a variety of positions and orientations, and likewise for $\{B_i\}$, so that the
%resulting $X$ is robust to measurement errors. 
This chapter is organized as follows. 
In Section~\ref{sec:sol_methods}, a detailed review is given for the existing methods that solve the $AX=XB$ problem using pairs of $\{A_{i}, B_{i}\}$ with correspondence. The notation used throughout the literature is not consistent and the authors strove %tried their best 
to standardize the notation used across the reviewed methods
\textcolor{blue}{to provide the readers with a straightforward and consistent representation of the methods and their relationships.} %so that readers can have a straightforward and consistent understanding of the methods and their relationships. 
Some approaches are preferable under certain circumstances and their advantages and disadvantages are also highlighted. 
In Section~\ref{sec:data_selection}, some important criterion for data selection and different errors metrics used in the literature are presented. 
%In section 5, numerical simulations are performed on the selected methods and further conclusions are given based on the results of the simulation. 
Finally, in Section~\ref{sec:conclusion} a complete summary of the $AX=XB$ solvers is provided and open problems are noted as well.

@@

The problem of solving Eq.~(\ref{mainaxxb}) for $X$ when multiple corresponding pairs of $A$s and $B$s are present has a history that stretches back more than a quarter of a century
\cite{chou1991finding, park1994robot,shiu1989calibration}, with the earliest proposed method introduced by Shiu \cite{shiu1987finding, shiu1989calibration} and Tsai \cite{tsai1989new}. \textcolor{blue}{Surprisingly,} applications involving this problem still remain active today \cite{kim,dai}. Shah \cite{shah2012overview} overviewed several different AX = XB methods qualitatively. Fassi and Legnani \cite{fassi2005hand} gave a geometric view of $AX=XB$ and discussed the over-constrained and singular conditions. A more complete list of the traditional $AX=XB$ solvers includes: the Shiu method \cite{shiu1989calibration}, the screw motion method \cite{chen91,zhao2006hand}, the Euclidean \textcolor{blue}{g}%G
roup method \cite{park1994robot,gwak2003numerical}, the quaternion method\cite{chou1988quaternions, chou1991finding, horaud1995hand}, the dual quaternion method \cite{daniilidis1996dual, daniilidis1999hand}, and the Kronecker method \cite{andreff1999line,andreff2001robot}. Several new optimization methods emerged recently such as the convex optimization method \cite{zhao2011hand}, some global optimization methods  \cite{seo2009branch,andreff2001robot,heller2014hand} and a structure from motion (SfM) approach \cite{schmidt2005calibration}. The SfM method deals with the case where a calibration target is not applicable and a scaling factor needs to be calibrated in addition to rotation and translation. The methods mentioned previously are all off-line methods where $X$ can be calculated given a complete list of data pairs. However, several online methods \textcolor{blue}{have been} %are 
proposed that are more preferable to real-time applications \cite{andreff1999line,angeles2000online,ackerman2014online}. All the methods above assume $\{A_i, B_i\}$ data pairs with correspondence. Probabilistic methods that deal with data pairs without correspondence are introduced in \cite{ackermanGSI, ackerman2014information}. In the follow sections, representatives of the above $AX=XB$ solvers will be reviewed in detail.

@@

The closed form expression for $R_{X}$ is:
\textcolor{blue}{Note: It is hard to \~n in the below equation and also the 2nd subscript on R$_X$}
\begin{equation}
R_{X} = \exp{(\widetilde{\nn}_{A}\beta)}R_{X_{P}}
\label{RotationCheng}
\end{equation}
where 
\begin{center}
$R_{X_{p}} =  \exp{(\widetilde{\nn}_{X}\theta_{X})}$\\
$\nn_{X} = \nn_{B} \times \nn_{A}$\\
$\theta_{X} = \rm atan2(|\nn_{B} \times \nn_{A}|,\nn_{B} \cdot \nn_{A})$\\
\end{center}
and $\beta$ is an arbitrary angle. Given a vector $\nn = \left( n_{1}, n_{2}, n_{3} \right)^{T} \in \mathbb{R}^{3}$, $\widetilde{\nn}$ is a skew-symmetric matrix defined as below:\\
\begin{equation}
\tilde{\nn}
=
\begin{pmatrix}
0 & -n_{3} & n_{2} \\
n_{3} & 0 & -n_{1} \\
-n_{2} & n_{1} & 0
\end{pmatrix}.
\end{equation}

Equation~(\ref{RotationCheng}) shows that $R_{x}$ has one degree of freedom which is determined by the angle $\beta$. Therefore, two relative arm motions are needed to generate two $(A_{i}, B_{i})$ data pairs in order to calculate the unique solution of $X$. Given two pairs of $A$s and $B$s, two equations can be obtained as:
\begin{subequations}
\begin{gather}
A_{1}X = XB_{1} \label{7a}\\
A_{2}X = XB_{2}.\label{7b}
\end{gather}
\end{subequations}
Instead of giving a closed-form solution, $R_{X}$ is calculated by solving for $\beta$ in Eq.~(\ref{CYD}), which is formulated \textcolor{blue}{as a system of linear equations obtained} by equating two \textcolor{blue}{instances of} Eq.~(\ref{RotationCheng}) that are obtained from data pairs $(A_{1}, B_{1})$ and $(A_{2}, B_{2})$:
\begin{equation}
CY = D.
\label{CYD}
%$${\color{red}(Detailed description of C and D?)}$$
\end{equation}
In Eq.~(\ref{CYD}), $Y = \big( \; \cos(\beta_{1}),\; \sin(\beta_{1}), \; \cos(\beta_{2}),\; 	\sin(\beta_{2}) \;\big)^{T}$ where $\beta_{1}, \, \beta_{2}$ correspond to Eq.~(\ref{7a}) and Eq.~(\ref{7b}) respectively,  $C \in \mathbb{R}^{9 \times 4}$ and $D \in \mathbb{R}^{9 \times 1}$ are determined from $\nn_{A_{1}}$, $\nn_{B_{1}}$, $\nn_{A_{2}}$, and $\nn_{B_{2}}$. The explicit expressions for $C$ and $D$ are given in Eq.~(44) of \cite{shiu1989calibration}.

@@

\begin{center}
$\mathcal{A} = (\nn_{A_{1}}, \nn_{A_{2}}, \nn_{A_{1}} \times \nn_{A_{2}}) \in \mathbb{R}^{3 \times 3}$\\
 $\mathcal{B} = (\nn_{B_{1}}, \nn_{B_{2}}, \nn_{B_{1}} \times \nn_{B_{2}}) \in \mathbb{R}^{3 \times 3} $\\
\textcolor{blue}{I corrected the format of the two below equations, please make sure they are still correct\\}
$\tilde{\nn}_{A_{1}} = \log(R_{A_{i}})/\|\log^\vee(R_{A_i})\|$\\
%(\log R_{A_{i}})^{\vee}||$\\
$\tilde{\nn}_{B_{1}} = \log(R_{B_{i}})/\|\log^\vee(R_{B_i})\|$
%(\log R_{B_{i}})^{\vee}||$.
\end{center}
The solution for $R_X$ is uniquely determined given two pairs of $(A_i, B_i)$, and the solution for $\ttt_{X}$ can be obtained using Eq.~(\ref{trans}) once $R_{X}$ is obtained.\\
\begin{comment}
\begin{equation}
\bigg(\begin{array}{lr}
R_{A_{1}} - I \\
R_{A_{2}} - I
\end{array}\bigg)\ttt_{X}=
\bigg(\begin{array}{lr}
R_{X}\ttt_{B_{1}} - \ttt_{A_{1}}\\
R_{X}\ttt_{B_{2}} - \ttt_{A_{2}}
\end{array}
\bigg)
\label{Lie_Translation}
\end{equation}
\end{comment}

>>>>

\author{Qianli Ma\\ 
		\textbf{Gregory S. Chirikjian}
    \affiliation{
	Robot and Protein Kinematics Laboratory\\
	Laboratory for Computational Sensing and Robotics\\
	Department of Mechanical Engineering\\
	The Johns Hopkins University\\
	Baltimore, Maryland, 21218\\
    Email: \{mqianli1, gchirik1\}@jhu.edu
    }	
}

@@

\keywords{ {\color{green}Sensor Calibration, Hand-Eye Calibration, Humanoid Robot, Review}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{nomenclature}
\entry{$SO(3)$}{$SO(3) \doteq \{R \, | \, RR^{T} = R^{T}R = \mathbb{I}$ %and
 $\det(R) = 1$ where $R \in \mathbb{R}^{3 \times 3}\}$}
\entry{$SE(3)$}{$SE(3) \doteq \{H \, | \, H=\left( R \;   \ttt ; {\bf 0}^{T} 1 \right) \in \mathbb{R}^{4 \times 4},$ where $R \in SO(3)$ and $\ttt \in \mathbb{R}^{3}\}$ }
\entry{$so(3)$}{$so(3) \doteq \{\Omega \,| \, R = exp(\Omega)$, where $\Omega \in \mathbb{R}^{3 \times 3}$ and $R \in SO(3)$ $\}$}
\entry{$se(3)$}{$se(3) \doteq \{\Xi \, | \, H = exp(\Xi)$, where $\Xi =\left(\Omega \; \xi; \; {\bf 0}^{T} 0 \right)$ and $\Omega \in so
(3), \, \xi \in \mathbb{R}^{3}, \, H \in SE(3) \}$}
\entry{$\exp()$}{The matrix exponential of a square matrix. }
\entry{$\log()$}{The matrix logarithm of a square matrix}
\entry{$H$}{A general rigid body transformation ($H \in SE(3)$) }
\entry{$\mathfrak{H}$}{ If $H$ is an element of a Lie Group, $\mathfrak{H}$ is the corresponding element in the Lie algebra}
\entry{$\mathbb{O}_n$}{$n \times n$ zero matrix}
\entry{$\mathbb{I}_n$}{$n \times n$ identity matrix}
\entry{$\{E_i\}$}{the set of ``natural" basis elements for Lie algebra}
\entry{$^\vee$}{For Lie algebra, the ``vee" operator is defined such that $\left(\displaystyle\sum\limits_{i=1}^n x_iE_i\right)^{\vee}\doteq(x_1,x_2,...,x_n)^T$ where $n = 3$ for $so(3)$ and $n = 6$ for $se(3)$}
\entry{$\widehat{}$}{For Lie algebra, the ``hat" operator is the inverse of the ``vee" operator. $\widehat{(x_1,x_2,...,x_n)^T} \doteq \left( \displaystyle\sum\limits_{i=1}^n x_iE_i \right)$; For a vector ${\bf n} \in \mathbb{R}^{3 \times 1}$. $\widehat{\bf n}$ represents the corresponding skew symmetric matrix }
\entry{$\circ$}{The operator defined for the group product}
\entry{$\odot$}{The operator defined for the quaternion product}
\entry{$\hat{\odot}$}{The operator defined for the dual quaternion product}
\entry{$\otimes$}{The operator defined for the Kronecker product}
\entry{$vec$}{The ``vec'' operator is defined such that $vec(A) = [a_{11},...,a_{1m},a_{21},...,a_{2m},...,a_{n1},...,a_{nm}]^{T}$ for $A = [a_{ij}] \in \mathbb{R}^{m \times n}$}
\entry{$A_i$}{A rigid body transformation ($A_i \in SE(3)$), associated with one sensor measurement source}
\entry{$B_i$}{A rigid body transformation ($B_i \in SE(3)$), usually associated with a different sensor measurement source}
\entry{$X$}{The rigid body transformation ($X %X_i 
\in SE(3)$) that relates $A_i$ to $B_i$}
\entry{$R_{H}$}{The rotation matrix of any general transformation matrix $H \in SE(3)$}
\entry{$\ttt_{H}$}{The translation vector of any general transformation matrix $H \in SE(3)$}
\entry{$\nn_{H}$}{The axis of rotation for $R_{H}$}
\entry{$\theta_{H}$}{The angle of rotation for $R_{H}$ about $\nn_{H}$}
\entry{$\rho$}{A probability distribution of $H\in G$, where G $\subset$ SE(3)}
\entry{$M$}{For $\rho$, $M$ is the mean of the distribution}
\entry{$\Sigma$}{For $\rho$, $\Sigma$ is the covariance of the distribution about the mean, $M$}
\entry{$Ad$}{For the Lie group $G$ and the Lie algebra $\mathfrak{G}$, the adjoint operator is the transformation\\ Ad: $G \rightarrow$ GL($\mathfrak{G}$), defined as\\ Ad($H_1$)$\mathfrak{H}_2 \doteq \frac{d}{dt}(H_1 \circ e^{t \mathfrak{H}_2} \circ H_1^{-1})$}
\entry{$Ad(H) $}{The adjoint matrix with columns $(H E_i H^{-1})^{\vee}$}
\end{nomenclature}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
\label{Intro}

@@

@@

\begin{figure}[t!]
\includegraphics[width=3.3in]{figure/AX=XB(ASME)_v1.png}
\centering
\caption{The $AX=XB$  Sensor Calibration Formulation}
\label{AXXBfig1}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics[width=3.3in]{Photos/UR5_Frame_Final.jpg}
\caption{Application of AX=XB in ultrasound sensor calibration: an ultrasound probe is attached to the end-effector and the calibration phantom is used for ultrasound probe calibration. (The UR5 robot pictured above is owned by Professor Emad Boctor of Johns Hopkins University)}
\label{AXXBfig2}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics[width=3.3in]{Photos/Robot_Patern_2.jpg}
\caption{Application of AX=XB in Humanoid Camera Sensor Calibration: The Humanoid Robot Named Atlas Designed by %the Company
 \textit{Boston Dynamics} Requires head-body calibration before turning the knob. Different pairs of $(A_i, B_i)$ are measured by changing the head pose of the humanoid robot. (This picture was generated using the open-source robot simulation software Gazebo)}
\label{AXXBfig3}
\end{figure}

Performing the matrix multiplication of homogeneous transformations in Eq.~(\ref{mainaxxb}) and separating out the rotational and translational parts results in two equations of the form:
\begin{subequations}
\begin{gather}
R_A R_X = R_X R_B \label{subequ1}\\
R_A {\bf t}_X + {\bf t}_A = R_X {\bf t}_B + {\bf t}_X \label{subequ2}.
\end{gather}
\label{axxb}
\end{subequations}
One strategy for solving Eq.~(\ref{mainaxxb}) reduces to first solving Eq.~(\ref{subequ1}) for only rotation and then rearranging Eq.~(\ref{subequ2}) to find acceptable values of ${\bf t}_X$ satisfying $ (R_A - \mathbb{I}_{3}) {\bf t}_X = R_X {\bf t}_B - {\bf t}_A$.
%One strategy to solve Eq.~(\ref{mainaxxb}) \textcolor{blue}{of data}would appear to reduce to first solving Eq.~(\ref{subequ1}) for only rotation and then rearranging Eq.~(\ref{subequ2}) so as to find acceptable values of ${\bf t}_X$ satisfying $ (R_A - \mathbb{I}_{3}) {\bf t}_X = R_X {\bf t}_B - {\bf t}_A. $  
The other strategy is to solve for $R_{X}$ and $\ttt_{X}$ simultaneously based on some cost function $f(R_{X}, \ttt_{X})$ or reformulating the matrix equation into a dual quaternion representation. %dual quaternion. 
However, when there are only two exact sensor measurements, there are some problems with the first  approach. As pointed out in \cite{park1994robot,shiu1989calibration}, in nondegenerate cases, there is a one-parameter set of solutions to Eq.~\ref{subequ1}%the first part in Eq.(\ref{subequ1})
, and the matrix $R_A - \mathbb{I}_{3}$ in general has a rank of $2$. Hence, there are two unspecified degrees of freedom to the
problem, and it cannot be solved uniquely unless additional measurements are taken.

@@

%A wide variety of such metrics are discussed in \cite{axxb13} that have the useful property of left-invariance, $d(H_0 H_1, H_0 H_2) = d(H_1, H_2)$ for any $H_0, H_1, H_2 \in SE(3)$.
%
%
%Perhaps the simplest of the left-invariant ones is based on the weighted Frobenius norm
%$$ d^2(H_1,H_2) = \|H_1 - H_2\|_{W}^{2} = {\rm trace}[(H_1 - H_2)W(H_1 - H_2)^T] $$
%where $W$ is a matrix that weights rotations and translations appropriately, as described in \cite{axxb13}.
%The sets of pairs $(A_i,B_i)$ for $i=1,2...,n$ is chosen such
%that the set $\{A_i\}$ is spread out over a variety of positions and orientations, and likewise for $\{B_i\}$, so that the
%resulting $X$ is robust to measurement errors. 
This chapter is organized as follows. 
In Section~\ref{sec:sol_methods}, a detailed review is given for the existing methods that solve the $AX=XB$ problem using pairs of $\{A_{i}, B_{i}\}$ with correspondence. The notation used throughout the literature is not consistent and the authors strove %tried their best 
to standardize the notation used across the reviewed methods
to provide the readers with a straightforward and consistent representation of the methods and their relationships. %so that readers can have a straightforward and consistent understanding of the methods and their relationships. 
Some approaches are preferable under certain circumstances and their advantages and disadvantages are also highlighted. 
In Section~\ref{sec:data_selection}, some important criterion for data selection and different errors metrics used in the literature are presented. 
%In section 5, numerical simulations are performed on the selected methods and further conclusions are given based on the results of the simulation. 
Finally, in Section~\ref{sec:conclusion} a complete summary of the $AX=XB$ solvers is provided and open problems are noted as well.

@@

The problem of solving Eq.~(\ref{mainaxxb}) for $X$ when multiple corresponding pairs of $A$s and $B$s are present has a history that stretches back more than a quarter of a century
\cite{chou1991finding, park1994robot,shiu1989calibration}, with the earliest proposed method introduced by Shiu \cite{shiu1987finding, shiu1989calibration} and Tsai \cite{tsai1989new}. Applications involving this problem still remain active today \cite{kim,dai}. Shah \cite{shah2012overview} overviewed several different AX = XB methods qualitatively. Fassi and Legnani \cite{fassi2005hand} gave a geometric view of $AX=XB$ and discussed the over-constrained and singular conditions. A more complete list of the traditional $AX=XB$ solvers includes: the Shiu method \cite{shiu1989calibration}, the screw motion method \cite{chen91,zhao2006hand}, the Euclidean group method \cite{park1994robot,gwak2003numerical}, the quaternion method\cite{chou1988quaternions, chou1991finding, horaud1995hand}, the dual quaternion method \cite{daniilidis1996dual, daniilidis1999hand}, and the Kronecker method \cite{andreff1999line,andreff2001robot}. Several new optimization methods emerged recently such as the convex optimization method \cite{zhao2011hand}, some global optimization methods  \cite{seo2009branch,andreff2001robot,heller2014hand} and a structure from motion (SfM) approach \cite{schmidt2005calibration}. The SfM method deals with the case where a calibration target is not applicable and a scaling factor needs to be calibrated in addition to rotation and translation. The methods mentioned previously are all off-line methods where $X$ can be calculated given a complete list of data pairs. However, several online methods have been 
proposed that are more preferable to real-time applications \cite{andreff1999line,angeles2000online,ackerman2014online}. All the methods above assume $\{A_i, B_i\}$ data pairs with correspondence. Probabilistic methods that deal with data pairs without correspondence are introduced in \cite{ackermanGSI, ackerman2014information}. In the follow sections, representatives of the above $AX=XB$ solvers will be reviewed in detail.

@@

The closed form expression for $R_{X}$ is:
\begin{equation}
R_{X} = \exp{(\hat{\nn}_{A}\beta)}R_{X_{P}}
\label{RotationCheng}
\end{equation}
where 
\begin{center}
$R_{X_{p}} =  \exp{(\widehat{\nn}_{X}\theta_{X})}$\\
$\nn_{X} = \nn_{B} \times \nn_{A}$\\
$\theta_{X} = \rm atan2(|\nn_{B} \times \nn_{A}|,\nn_{B} \cdot \nn_{A})$\\
\end{center}
and $\beta$ is an arbitrary angle. Given a vector $\nn = \left( n_{1}, n_{2}, n_{3} \right)^{T} \in \mathbb{R}^{3}$, $\widehat{\nn}$ is a skew-symmetric matrix defined as below:\\
\begin{equation}
\widehat{\nn}
=
\begin{pmatrix}
0 & -n_{3} & n_{2} \\
n_{3} & 0 & -n_{1} \\
-n_{2} & n_{1} & 0
\end{pmatrix}.
\end{equation}

Equation~(\ref{RotationCheng}) shows that $R_{x}$ has one degree of freedom which is determined by the angle $\beta$. Therefore, two relative arm motions are needed to generate two $(A_{i}, B_{i})$ data pairs in order to calculate the unique solution of $X$. Given two pairs of $A$s and $B$s, two equations can be obtained as:
\begin{subequations}
\begin{gather}
A_{1}X = XB_{1} \label{7a}\\
A_{2}X = XB_{2}.\label{7b}
\end{gather}
\end{subequations}
Instead of giving a closed-form solution, $R_{X}$ is calculated by solving for $\beta$ in Eq.~(\ref{CYD}), which is formulated as a system of linear equations obtained by equating two instances of Eq.~(\ref{RotationCheng}) that are obtained from data pairs $(A_{1}, B_{1})$ and $(A_{2}, B_{2})$:
\begin{equation}
CY = D.
\label{CYD}
%$${\color{red}(Detailed description of C and D?)}$$
\end{equation}
In Eq.~(\ref{CYD}), $Y = \big( \; \cos(\beta_{1}),\; \sin(\beta_{1}), \; \cos(\beta_{2}),\; 	\sin(\beta_{2}) \;\big)^{T}$ where $\beta_{1}, \, \beta_{2}$ correspond to Eq.~(\ref{7a}) and Eq.~(\ref{7b}) respectively,  $C \in \mathbb{R}^{9 \times 4}$ and $D \in \mathbb{R}^{9 \times 1}$ are determined from $\nn_{A_{1}}$, $\nn_{B_{1}}$, $\nn_{A_{2}}$, and $\nn_{B_{2}}$. The explicit expressions for $C$ and $D$ are given in Eq.~(44) of \cite{shiu1989calibration}.

@@

\begin{center}
$\mathcal{A} = (\nn_{A_{1}}, \nn_{A_{2}}, \nn_{A_{1}} \times \nn_{A_{2}}) \in \mathbb{R}^{3 \times 3}$\\
 $\mathcal{B} = (\nn_{B_{1}}, \nn_{B_{2}}, \nn_{B_{1}} \times \nn_{B_{2}}) \in \mathbb{R}^{3 \times 3} $\\
$\tilde{\nn}_{A_{1}} = \log(R_{A_{i}})/\|\log^\vee(R_{A_i})\|$\\
%(\log R_{A_{i}})^{\vee}||$\\
$\tilde{\nn}_{B_{1}} = \log(R_{B_{i}})/\|\log^\vee(R_{B_i})\|$.
%(\log R_{B_{i}})^{\vee}||$.
\end{center}
The solution for $R_X$ is uniquely determined given two pairs of $(A_i, B_i)$, and the solution for $\ttt_{X}$ can be obtained using Eq.~(\ref{trans}) once $R_{X}$ is obtained.\\
\begin{comment}
\begin{equation}
\bigg(\begin{array}{lr}
R_{A_{1}} - I \\
R_{A_{2}} - I
\end{array}\bigg)\ttt_{X}=
\bigg(\begin{array}{lr}
R_{X}\ttt_{B_{1}} - \ttt_{A_{1}}\\
R_{X}\ttt_{B_{2}} - \ttt_{A_{2}}
\end{array}
\bigg)
\label{Lie_Translation}
\end{equation}
\end{comment}

\subsubsection{Estimation of X Using Multiple Pairs with Noise}
When there are multiple pairs of $(A_{i}, B_{i})$ with noise, rotation matrix $R_{X}$ is solved for first and then the translation vector $\ttt_{x}$ is obtained using a least squares method given known $R_{X}$. The closed-form expression for $R_{X}$ is as follows:
\begin{equation}
R_{X} = (M^{T}M)^{-\frac{1}{2}}M^{T}
\end{equation}
where \\
\begin{center}
$M = \sum_{i=1}^{n}{\nn_{B_{i}} \nn_{A_{i}}^{T}}$.
\end{center}
Note that $i \geq 3$ is a necessary condition for $M$ to be a non-singular matrix, but it does not guarantee $M$ to be nonsingular. Theoretically, the Lie group method is more likely to fail when the number of data pairs is small, i.e., close to 3 pairs,  while in real application, failure is rarely %this is barely 
seen as long as the data pairs are not specially chosen such that $M$ is degenerate. Given known $R_{X}$, $\ttt_{X}$ can be calculated using the least squares method shown in Eq.~(\ref{t_least}):
